SmartCheck: Automatic and Efficient Counterexample Reduction and Generalization

### 2013-01-27 paper/paper.tex
paper updates.

\usepackage{ifthen}
\newboolean{submission}  %set to true for the submission version
%\setboolean{submission}{false}
\setboolean{submission}{true}
\ifthenelse
{\boolean{submission}}
{ \newcommand{\todo}[1]{ } } %hide todo
{ \newcommand{\todo}[1]{ {\color{blue}$<<$#1$>>$}
 }}
%\usepackage{fancyhdr}

@@

\todo{define variant, tag}
\todo{note constants are user-defined arguments, other simplifications}
\todo{thread args through}
\todo{termination for each algorithm}
\todo{fromMaybe over pattern matching?}

@@

\noindent
In Section~\ref{experiments}, we discuss some of our experiences with using
SmartCheck, including checking properties from Xmonad.

@@

The number of constructors in an algebraic data value primarily determines how
large and understandable it is.  In our experience, the size of fields that come
from primitive types, like \ttp{Int} or \ttp{Char}, have less of a role in
understanding a counterexample.  However, a testing algorithm might spend
significant time testing new values in which primitive types are reduces.

@@

We therefore introduce another kind of generalization we call \emph{existential
  sub-value generalization}.  In this generalization, if there a counterexample
containing every possible variant as a sub-value, then we abstract it.  For
example, the following all characterize counterexamples:
%
\begin{code}
forall x . Div x (Add (C (-5)) (C 5))
forall x . Div x (C 0)
forall x . Div x (Div (C 0) (C 1))
\end{code}
%
\noindent
Because there are only three variants in the type, we have found counterexamples
built from each of them in the divisor.  We therefore return a formula like the
following:
%
\begin{code}
forall values x .
  forall constructors C\(\sb{0}\) .
    there exist arguments \(\stackrel{\rightarrow}{y}\) .
      such that Div x (C\(\sb{0} \stackrel{\rightarrow}{y}\))
\end{code}
%

@@

\todo{avoid complexities
  \url{http://stackoverflow.com/questions/14006005/idiomatic-way-to-shrink-a-record-in-quickcheck}}
\cite{}

>>>>

\usepackage{ifthen}
\newboolean{submission}  %set to true for the submission version
\setboolean{submission}{false}
%\setboolean{submission}{true}
\ifthenelse
{\boolean{submission}}
{ \newcommand{\todo}[1]{ } } %hide todo
{ \newcommand{\todo}[1]{ {\color{blue}$<<$#1$>>$}
 }}
%\usepackage{fancyhdr}

@@

\todo{define variant, tag}
\todo{note constants are user-defined arguments, other simplifications}
\todo{thread args through}
\todo{termination for each algorithm}
\todo{fromMaybe over pattern matching?}
\todo{show quantification in intro}
\todo{benchmark feat}

@@

\noindent
In Section~\ref{sec:experiments}, we discuss some of our experiences with using
SmartCheck, including checking properties from Xmonad.

@@

\todo{correspond to dimension 0 from\cite{agata}}
The number of constructors in an algebraic data value primarily determines how
large and understandable it is.  In our experience, the size of fields that come
from primitive types, like \ttp{Int} or \ttp{Char}, have less of a role in
understanding a counterexample.  However, a testing algorithm might spend
significant time testing new values in which primitive types are reduces.

@@

We therefore introduce another kind of generalization we call \emph{existential
  sub-value generalization}.  In this generalization, if there a counterexample
containing every possible variant as a sub-value, then we abstract it.  For
example, the following all characterize counterexamples:
%
\begin{code}
Div (C 7) (Add (C (-5)) (C 5))
Div (Add (C 3) (C 2)) (C 0)
Div (C (-2)) (Div (C 0) (C 1))
\end{code}
%
\noindent
Because there are only three variants in the type, we have found counterexamples
built from each of them in the divisor.  We therefore return a formula like the
following:
%
\begin{code}
forall values x .
  forall constructors C\(\sb{0}\) .
    there exist arguments \(\stackrel{\rightarrow}{y}\) .
      such that Div x (C\(\sb{0} \stackrel{\rightarrow}{y}\))
\end{code}
%

@@

Closely related to SmartCheck is the recent Haskell library Feat.  Feat
enumerates algebraic data types in Haskell and indexing them
quickly~\cite{feat}.  For example, Feat returns the $10^{1000}$ value in the
enumeration of lists of Booleans in under a second.  Feat combines some of the
advantages of SmallCheck and QuickCheck:

Feat provides a functional representation of enumerations,
allowing for fast indexing of large values in an enumeration.

\todo{avoid complexities \url{http://stackoverflow.com/questions/14006005/idiomatic-way-to-shrink-a-record-in-quickcheck}%
%
The SYB paper:%
  \url{http://research.microsoft.com/en-us/um/people/simonpj/Papers/hmap/index.htm}%
  Has shrink example%
%
* QuickSpec:%
  \url{http://www.cse.chalmers.se/~nicsma/quickspec.pdf}%
%
\url{http://blog.regehr.org/archives/697} --- check out C-reduce (Regehr) and Delta%
  debugging (\url{http://www.st.cs.uni-saarland.de/dd/}).  C-reduce is in PLDI.%
%
* Also check out \url{http://www.whyprogramsfail.com/}%
%
* GenCheck \url{https://github.com/JacquesCarette/GenCheck}%
%
* Dart-check: \url{http://code.google.com/p/dart-immutable/} (and G+ post by Paul%
  Brauner)%
}
